---
title: "Summarize the Swedish parliamentary election results in 2022 in a user-friendly interface"
author: "Chandika Nishshanka & Ayesha Gamage"
data: "'r.sys.date()'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ParliamentElectionResult2022)
```
## Introduction

The Swedish parliamentary elections in 2022 have produced a wealth of data that is vital for understanding the political landscape and trends. To make this information more accessible and user-friendly, we have developed a specialized tool using R package with Shiny App that allows you to easily summarize and analyze the election results.

## Package Overview

The package provides three primary functions:

1. `election_summary`: This function retrieves summary data for the entire country's parliamentary election results in 2022. It offers a high-level overview of the election outcomes.

2. `election_result`: With this function, you can obtain detailed election results for a specific county by specifying its county code as an input parameter.

3. `showElectionData`: This function launches a Shiny application that facilitates interactive exploration and analysis of the election data.

In the following sections, we will delve into each function's usage and demonstrate how to extract valuable insights from the Swedish parliamentary election results.

## Function: `election_summary`

The `election_summary` function provides a quick summary of the 2022 parliamentary election results for the entire country. It aggregates data related to party votes, allowing you to get a broad view of the election outcome.



### Example usage of election_summary
```r
summary_data <- election_summary()
```

### Example usage of election_result
```r
county_code <- "01"  # Replace with the desired county code
county_data <- election_result(county_code)
```

### Example usage of showElectionData
```r
showElectionData()
```
## Features

The Shiny app consists of the following key features:

1. **Summary Tab:** Provides a high-level summary of the election results for the entire country, including a bar chart displaying the top parties and a table with relevant statistics.

2. **Graph Tab:** Allows users to select a specific parliamentary constituency from a dropdown menu and view a bar chart representing the election results for that constituency.

3. **Data Tab:** Similar to the Graph tab, this tab allows users to select a parliamentary constituency and view detailed data in tabular format.

4. **Reference Tab:** Offers additional information and references to the data sources.

## Conclusion

The "Swedish Parliamentary Election 2022 Shiny App" offers a convenient and interactive way to explore and analyze the election results.
